Verifying Demonstrations

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Adds \paragraph to delimit MF, DH, TF proofs
Improves SimTF proof for UWB

@@

@@

The last property is \ac{DBTF}.
The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives both responses to the accomplice, the 
accomplice can compute his secret key.
And any help will increase the probability of success of future attempts.

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
\end{theorem}

\begin{proof}
  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
  with non-negligible probability~\(\epsilon\) better than guessing, \ie a 
  success probability of \(\frac{1}{m^n}+\epsilon\).
  Say that \(\adv\) has successfully authenticated with the prover's help and 
  \(\S\) is given \(\adv\)'s state.

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
  independent (uniformly random), the help provided by the prover must be 
  independent of the chosen challenge.

  Now \(\adv\) will provide a correct response with \(\frac{1}{m^n}+\epsilon\) 
  probability.
  When \(S\) has the correct response it can compute the secret of the prover 
  using the two known correct responses and thus authenticate to the verifier 
  with probability \(p_{\S} = 1\) in any successive session.
  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
\end{proof}

>>>>

\paragraph{\Acl{DBMF}}

@@

\paragraph{\Acl{DBDH}}

@@

\paragraph{\Acl{DBTF}}

The last property is \ac{DBTF}.
The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives more than one response to the accomplice, 
the accomplice can compute the secret key and, thus, impersonate forever.
And any help will increase the probability of success of future attempts.

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} = 0\).
\end{theorem}

\begin{proof}
  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
  Say that \(\adv\) has successfully authenticated with the prover's help and 
  \(\S\) is given \(\adv\)'s state.

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover without tainting the 
  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
  provided by the prover must be independent from the chosen challenge.
  Now \(\adv\) will provide a correct response with probability~\(p_{\adv}\).
  Hence, \(p_{\S} = p_{\adv}\).
\end{proof}
